### 2013-09-13 mr_background.tex
updated new refs and anatomy background

\subsection{Functional MR Sequences}
Even though T2WI is the mainstay of prostate MR, its overall performance in
prostate cancer diagnosis is not optimal. The incorporation of two or more
functional sequences in multiparametric MR imaging (mpMRI) has been shown to
significantly improve the performance of MRI in cancer
diagnosis.~\cite{Turkbey2012} In fact, the European Society of Urogenital
Radiology’s (ESUR) prostate MR guidelines recommend at least 2 functional
imaging techniques in addition to T2WI in order to better characterize prostate
tumors.8 In a study by Turkbey et al, researchers found that mpMRI had a
positive predictive value of 98\% in prostate cancer
detection.~\cite{Turkbey2012} Functional sequences include diffusion- weighted
imaging (DWI), dynamic contrast enhanced imaging (DCE-MRI) and MR spectroscopic
imaging (MRSI).

>>>>

\subsection{Functional MR Sequences}
Even though T2WI is the mainstay of prostate MR, its overall performance in
prostate cancer diagnosis is not optimal. The incorporation of two or more
functional sequences in multiparametric MR imaging (mpMRI) has been shown to
significantly improve the performance of MRI in cancer
diagnosis.~\cite{Turkbey2012} In fact, the European Society of Urogenital
Radiology’s (ESUR) prostate MR guidelines recommend at least 2 functional
imaging techniques in addition to T2WI in order to better characterize prostate
tumors.~\cite{Barentsz2012} In a study by Turkbey et al., researchers found that mpMRI had a
positive predictive value of 98\% in prostate cancer
detection.~\cite{Turkbey2012} Functional sequences include diffusion- weighted
imaging (DWI), dynamic contrast enhanced imaging (DCE-MRI) and MR spectroscopic
imaging (MRSI).
